A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-08-26 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
Small revision

However, oracles are expensive and there are other usecases for connecting a contract with traditional software. One example is
automating procedures like managing an auction,  bidding in
an auction, optimizing fees, or initiating delivery of goods to a
customer. While some of these procedures are amenable to
implementation as contracts, we might want to save the fee of running
them on the blockchain. In particular, for actions that happen
strictly within a single domain of trust, it is not worth running them
on the blockchain. For example, automated bidding runs on behalf of
a single peer.

@@

The execution model consists of functional (OCaml) programs that
interact with an abstraction of the Tezos blockchain
\cite{tezos-whitepaper}. As the blockchain is realized by a
peer-to-peer network of 
independent nodes, interaction happens through
\emph{local nodes} that receive requests to originate and invoke
contracts from programs that run on a particular node. We model the blockchain
itself as a separate, abstract global entity that represents the
current consensual state of the system. Our model does not express
low-level details, but relies on nondeterminism to describe
the possible behaviors of the system. In particular, we do
\textbf{not} formalize the execution of the smart contracts
themselves, we rather consider them as black boxes and probe their
observable behavior. Tezos' smart contract language Michelson and its
properties have been formalized elsewhere \cite{DBLP:conf/fm/BernardoCHPT19}.

@@

For all $\OPH\in\DOM (\PENDING)$,
if  $\PENDING (\OPH) =  \Angle{\OP, \hat\TIME, \STATUS}$
\begin{itemize}
\item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then \\
  $\PUK, \PUK'$ $\in$ $\DOM (\MANAGERS)$;
\item if $\OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ$, then
  \begin{itemize}
  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH\in$$\DOM (\CONTRACTORS)$,
  \item $\JTypeValue\PARAMETER{ \TYPE_p}$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$;
  \end{itemize}
\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
  \STATUSINCLUDED\ \TIME'$, then
  \begin{itemize}
  \item $\PUK \in \DOM (\MANAGERS)$ and  $\PUH =\GENERATEHASH (\CODE, \TIME') \in \DOM (\CONTRACTORS)$,
  \item $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$,  $\JTypeCode\CODE{
      \TPAIR\ \TYPE_p\ \TYPE_s}$ and $\JTypeValue\STRING{ \TYPE_s}$.
  \end{itemize}
\end{itemize}
\end{lemma}

@@

\section{Related Work}
\label{sec:related work}
The inability to access external data sources limits the potential of
smart contracts. Oracles
\cite{oracle-patterns,call-action-oracle,oracles-study} can help
overcome this limitation by providing a bridge between the outside
sources and the blockchain network. A blockchain oracle is used to
provide external data to smart contracts. There has been extensive research on providing oracle solutions for blockchain.  Adler et al
\cite{blockchain-oracles} propose a framework to explain blockchain
oracles and various key aspects of oracles. This framework aims to
provide developers with a guide for incorporating oracles into
blockchain-based applications. The main problems with using a blockchain oracle are the untrusted
data provided maliciously or inaccurately \cite{trustworthy}. Ma at el
\cite{reliable-oracle} propose an oracle equipped with 
verification and disputation mechanisms. Similarly, Lo et al
\cite{reliablity-oracles} provide a framework for performing
reliability analysis of various blockchain oracle platforms.

>>>>

%However, oracles are expensive and 
There are other usecases for connecting a contract with traditional software. One example is
automating procedures like managing an auction,  bidding in
an auction, optimizing fees, or initiating delivery of goods to a
customer. While some of these procedures are amenable to
implementation as contracts, we might want to save the fee of running
them on the blockchain. In particular, for actions that happen
strictly within a single domain of trust, it is not worth running them
on the blockchain. For example, automated bidding runs on behalf of
a single peer.

@@

The execution model consists of functional (OCaml) programs that
interact with an abstraction of the Tezos blockchain
\cite{tezos-whitepaper}. As the blockchain is realized by a
peer-to-peer network of 
independent nodes, interaction happens through
\emph{local nodes} that receive requests to originate and invoke
contracts from programs that run on a particular node. We model the blockchain
itself as a separate, abstract global entity that represents the
current consensual state of the system. Our model does not express
low-level details, but relies on nondeterminism to describe
the possible behaviors of the system. In particular, we do
\textbf{not} formalize the execution of the smart contracts
themselves, we rather consider them as black boxes and probe their
observable behavior. Tezos's smart contract language Michelson and its
properties have been formalized elsewhere \cite{DBLP:conf/fm/BernardoCHPT19}.

@@

For all $\OPH\in\DOM (\PENDING)$,
if  $\PENDING (\OPH) =  \Angle{\OP, \hat\TIME, \STATUS}$
\begin{itemize}
\item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then \\
  $\PUK, \PUK'$ $\in$ $\DOM (\MANAGERS)$;
\item if $\OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ$, then
  \begin{itemize}
  \item $\PUK \in \DOM (\MANAGERS)$ and $\PUH \in\DOM (\CONTRACTORS)$,
  \item $\JTypeValue\PARAMETER{ \TYPE_p}$ where $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$;
  \end{itemize}
\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS = \STATUSINCLUDED\ \TIME'$, then
  \begin{itemize}
  \item $\PUK \in \DOM (\MANAGERS)$ and  $\PUH =\GENERATEHASH (\CODE, \TIME') \in \DOM (\CONTRACTORS)$,
  \item $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$,  $\JTypeCode\CODE{
      \TPAIR\ \TYPE_p\ \TYPE_s}$ and $\JTypeValue\STRING{ \TYPE_s}$.
  \end{itemize}
\end{itemize}
\end{lemma}

@@

\section{Related Work}
\label{sec:related work}
The inability to access external data sources limits the potential of
smart contracts. Oracles
\cite{oracle-patterns,call-action-oracle,oracles-study} can help
overcome this limitation by providing a bridge between the outside
sources and the blockchain network. A blockchain oracle is used to provide external data for smart contracts. When the external data is available, an oracle invokes a smart contract with that information. The invocation can conveniently be made through a programmatic interface. There has been extensive research on providing oracle solutions for blockchain.  Adler et al
\cite{blockchain-oracles} propose a framework to explain blockchain
oracles and various key aspects of oracles. This framework aims to
provide developers with a guide for incorporating oracles into
blockchain-based applications. The main problems with using a blockchain oracle are the untrusted
data provided maliciously or inaccurately \cite{trustworthy}. Ma at el
\cite{reliable-oracle} propose an oracle equipped with 
verification and disputation mechanisms. Similarly, Lo et al
\cite{reliablity-oracles} provide a framework for performing
reliability analysis of various blockchain oracle platforms.
